ZCB Pricing

### 2018-08-08 ZCB Pricing .Rmd
Comment changes

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
      sim_path[j,i] =sim_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

  # Monte Carlo Simulations
  Sum = colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
  Sum.= colSums(sim_path_inv[2:(s+1),]*dt)
  int = exp(-Sum.) #Exponential of the estimate
  int.= exp(-Sum) #Exponential of the estimate under the negative rv 
  mean_1 = mean(int) # Estimate using Z_i
  mean_2 = mean(int.)  # Estimate using -Z_i
  result = (mean_1+mean_2)/2 # Final estimate
  result

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z=rnorm(n)
  z_m= z-mean(z) # Moment matching transformation of RV to match finite moments

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] # Simulate rates using the transformed rv 
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
  h <- sqrt(beta^(2)+2*sigma^(2))
  A <-(2*h*exp((beta+h)*(T-t)/2)/(2*h+(beta+h)*(exp((T-t)*(h))-1)))^((2*alpha)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(beta+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r)
}

@@

}
# Therefore the control variates estimate:

Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=100){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r)
}

@@

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity", xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[4,2:9], col="red",type = "p", pch = 19)
lines(1:8, senses[5,2:9],col ="blue",type = "p", pch = 19)
legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)

plot(x=1:8,y=senses[1,2:9], ylim =c(0.55,0.7), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma", xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[6,2:9], col="red",type = "p", pch = 19)
lines(1:8, senses[7,2:9],col ="blue",type = "p", pch = 19)
legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)

@@

for ( i in 1:100){
  CR[i]=Crude_Monte_Carlo()
  #AN[i]=Antithetic_variates()
  #MM[i]=Moment_Matching()
  CV[i]=Control_Variates_estimate()
}

>>>>

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for the use of -Z_i
      sim_path[j,i] =sim_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

  # Monte Carlo Simulations
  Sum = colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
  Sum.= colSums(sim_path_inv[2:(s+1),]*dt)
  int = exp(-Sum.) #Exponential of the estimate using Z_i
  int.= exp(-Sum) #Exponential of the estimate using -Z_i
  mean_1 = mean(int) # Estimate using Z_i
  mean_2 = mean(int.)  # Estimate using -Z_i
  result = (mean_1+mean_2)/2 # Final estimate is taken as the average of the two estimates.
  result

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z=rnorm(n)
  z_m= z-mean(z) # Moment matching transformation of Z_i to match finite moments

  # Follow the same process as in the Monte Carlo approach , but use the transformed Z_i's to simulate the rates
  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] 
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

# Make use of the CIR model as the control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
  h <- sqrt(beta^(2)+2*sigma^(2))
  A <-(2*h*exp((beta+h)*(T-t)/2)/(2*h+(beta+h)*(exp((T-t)*(h))-1)))^((2*alpha)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(beta+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r)
}

@@

}
# The control variate estimate is taken as the difference between the the Crude MOnte carlo estimates of the Vasicek and CIR model plus the closed form of the CIR model

Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=100){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)- CIR_MC(alpha,beta,sigma,T,r,n,s)+bond_price_CIR(alpha,beta,sigma,t,T,r)
}

@@

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[4,2:9], col="red",type = "p")
lines(1:8, senses[5,2:9],col ="blue",type = "p")
legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[6,2:9], col="red",type = "p")
lines(1:8, senses[7,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

@@

for ( i in 1:100){
  CR[i]=Crude_Monte_Carlo()
  AN[i]=Antithetic_variates()
  MM[i]=Moment_Matching()
  CV[i]=Control_Variates_estimate()
}
